---
output: github_document
---

<!-- README.md is generated from README.Rmd. 
     Please edit that file and use `devtools::build_readme()` to rebuild README.md -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# probabilityDistributions

<!-- badges: start -->
[![R-CMD-check](https://github.com/PRIMER-e/probabilityDistributions/workflows/R-CMD-check/badge.svg)](https://github.com/PRIMER-e/probabilityDistributions/actions)
[![Codecov test coverage](https://codecov.io/gh/PRIMER-e/probabilityDistributions/branch/main/graph/badge.svg)](https://app.codecov.io/gh/PRIMER-e/probabilityDistributions?branch=main)
<!-- badges: end -->

The goal of probabilityDistributions is to provide a library of useful
probability distributions for both R and Stan.

## Installation

You can install the development version of probabilityDistributions from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PRIMER-e/probabilityDistributions")
```

## Example

This is a basic example which shows you how to calculate a Zero-Inflated
Poisson (ZIP) probability mass using both R and Stan:

```{r example}
library(probabilityDistributions)

stan_model_code <- paste0("functions { ", stan_probability_distribution("zi_poisson_lpmf"), " }")

model_listing <- rstan::stanc(model_code = stan_model_code)

stan_function_names <- rstan::expose_stan_functions(model_listing)

print(stan_function_names)

zi_poisson_lpmf(5, 7.5, 0.2)

dzip(5, 7.5, 0.2, log = TRUE)
```

## Development

After making changes run the following command before committing to rebuild
the package readme, which is also the home page.

```{r, eval = FALSE}
devtools::build_readme()
```
